---
title: "Tableau style Storyboards in R"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    # source: embed
    runtimme: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(quantmod)   # get stock prices; useful stock analysis functions
library(xts)        # working with extensible time series 
library(tidyverse) 
library(data.table)
library(shiny)
library(ggplot2)

loandf <- data.frame(fread("loandata_for_dashboard.csv",
                           stringsAsFactors = FALSE))
loandf <- loandf[1:16000,]

end_date <- as.character(Sys.Date() - 1) 


# get stockdata for facebook:
getSymbols.yahoo('FB', env = globalenv(), return.class = 'xts', 
                 from = '2013-01-01', 
                 to = end_date)
```



### Dygraphs - Perfect for charting interactive time-series data in R. Used here for plotting facebook stock data.

```{r}
library(dygraphs)
# dygraph(nhtemp, main = "New Haven Temperatures") %>% 
#   dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))

dygraph(FB, main = "Facebook Stock Price 2013 - present") %>% 
  dyRangeSelector(dateWindow = c("2013-01-01", end_date))
```

***

Explanation:

1) We use the package dygraphs to plot a timeseries object. In this case, it is the stock value for Facebook. (ticker symbol = FB)

2) Move the slider in the bottom to select the timeframe of interest.

3) Hover on the timeseries line to see exact values of the stock on a particular date.

4) Note that the latest Facebook stock data itself is pulled in from Yahoo! website using the quantmod package function - getSymbols.yahoo() 



### Graph of loan interest rates based on loan grade. See how the interest rates increase with a worse grade.

```{r}
# library(leaflet)
# leaflet() %>%
#   addTiles() %>%
#   addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")


qplot(loandf$int_rate, loandf$grade, xlab = "Loan interest Rate",
      ylab = "Loan Grade (A to  G)")
```

***

The loan grades are rated on a scale of A to G, with A being the least risky and G being the highest probability of defaults.






### Plotly - leverages the plotly.js library to convert ggplot2 graphics into interactive web-friendly versions.

```{r}
# library(plotly)
# p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
#             geom_bar(position = "dodge")
# ggplotly(p)


library(plotly)
p <- ggplot(data = loandf, aes(x = grade, fill = empl)) +
            geom_bar(position = "dodge")
ggplotly(p)
```

***

Interaction:

1) The usage of package ggplot2 allows us to convert graphs to interactive, data rich visuals perfect for presentations or publishing on the web! 
The tooltips can be used to convey additional data. 

2) Hover over the graph to see more details. Or use the icons to zoom in/out , save the image and much more!




### d3heatmap - Interactive heatmaps.

```{r}
library(d3heatmap)
d3heatmap(mtcars, scale="column", colors="Reds")
```

***

Interaction with Heatmap:

1) To view the heatmap in more details, click on any row or column by clicking axis labels.

2) Hover over any of the cells to see the values.

3) The use of d3heatmap package allows us to see the dendograms (tree chart). 
So from left to right, the cars were classified by the values on the x-axis. 
Hence we first divide the cars by number of cylinder (4 or 6), then each cylinder type is further divided by Transmission (am variable - 0 for automatic or 1 for manual), then V/S (0 or 1), and so on.









